Blum axioms and nondeterministic computation of functions

### 2016-03-22 paper.tex
paper.tex: Alter some words in the introduction.

In Theory of Computation,
we usually use languages
to mathematically model problems in the real world.
Decision problems (``yes/no'') are mapped to languages in a very natural way:
just put every ``yes'' instance in the language,
and leave the rest out.
Search problems usually are rewritten as a decision problem,
and then this problem is converted to a language.
For instance,
the task of finding a satisfying assignment for a Boolean formula $\phi$
is reinterpreted to the task of merely deciding whether this assignment exists,
and this task is then converted to a language
--- in this example we have $\SAT$, the Boolean satisfiability problem.
This does the trick when it comes to proving that something is hard;
for instance, if we show that the decision problem is $\NP$-hard or undecidable,
then intuitively the corresponding search problem must be at least as hard.
Therefore,
concepts like ``decidable'', ``$\NP$-complete'', ``polynomial-time computable''
only arise in the context of decision problems.

@@

This paper presents several attempts to establish
how a nondeterministic Turing machine can compute a function,
and to extend the concept of ``polynomial-time computable'' under each definition.
Sections \ref{sec:godel_numberings} and~\ref{sec:blum-axioms} sets reasonableness criteria
to both the definition of function computation and complexity of the computation.
Section~\ref{sec:nondeterministic_computation_of_functions}
presents and criticizes the several definitions.

>>>>

In Theory of Computation,
we usually use languages
to mathematically model problems in the real world.
Decision problems (``yes/no'') are mapped to languages in a very natural way:
just put every ``yes'' instance in the language,
and leave the rest out.
Search problems usually are rewritten as a decision problem,
and then this problem is converted to a language.
For instance,
the task of finding a satisfying assignment for a Boolean formula $\phi$
is reinterpreted to the task of merely deciding whether this assignment exists,
and this task is then converted to a language
--- in this example we have $\SAT$, the Boolean satisfiability problem.
This does the trick when it comes to proving that something is hard;
for instance, if we show that the decision problem is $\NP$-hard or undecidable,
then intuitively the corresponding search problem must be at least as hard.
Therefore,
concepts like ``decidable'', ``$\NP$-complete'', ``polynomial-time decidable''
arise naturally in the context of decision problems.

@@

This paper presents several attempts to establish
how a nondeterministic Turing machine could compute a function,
and to extend the concept of ``polynomial-time computable'' under each definition.
Sections \ref{sec:godel_numberings} and~\ref{sec:blum-axioms} sets reasonableness criteria
to both the definition of function computation and complexity of the computation.
Section~\ref{sec:nondeterministic_computation_of_functions}
presents and criticizes the several definitions.
